---
title: ""
author: 
date: 
output:
    bookdown::word_document2: 
      reference_docx: word-styles-reference.docx #make sure this line is indented! see this guide for formatting: https://rmarkdown.rstudio.com/articles_docx.html
      #reference_docx: word-styles-reference-singlespace.docx #make sure this line is indented! see this guide #pdf_document: 

#bibliography: INvenTree-metadata-analysis.bib #change this to the relevant .bib file placed in the same folder
suppress-bibliography: false
#csl: journal-of-ecology.csl #change this to the relevant csl file placed in the same folder
#nocite: |
#  @koulgi_extensive_2019, @pradhan_biocultural_2020, @page_climatic_2020
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Display items


## Tables



## Figures
fig_dataset<-"1"

#SI figure numbers

# Legends

#https://github.com/EcoClimLab/Operations/blob/master/Data_Management-Scientific_Workflow/manuscript_prep_with_Rmd.md
```
```{r read files, echo=F}
# Read in files
```
**Title: **

# **Authors:** {-}

Krishna Anujan ^1,2,3^* (ORCiD: 0000-0003-3604-5895)   

# Affiliations: {-}

^1^ India Tree Inventory Network, National Centre for Biological Sciences, TIFR, Bellary Road, Bengaluru 560065, India  
^2^ Smithsonian National Zoo and Conservation Biology Institute, 1500 Remount Road, Front Royal, Virginia 22303, USA  
^3^ Smithsonian Environmental Research Centre, Edgewater, Maryland, USA  

*corresponding author: krishna.anujan@gmail.com

# Abstract {-}


# Keywords {-}

\newpage

# Introduction {-}



# Materials and Methods {-}

## Study area {-}



# Results {-}


# Discussion {-}


# Acknowledgements {-}

# Conflict of Interest Statement {-}

# Data Accessibility Statement {-}


\newpage
# References {-}


